### 2016-11-10 paper/evaluation.tex
Updated RQs

\newcommand{\RQB}{How often do developers use low-level parallelism
to improve runtime performance?}

@@

\newcommand{\rqOne}{\textbf{RQ1.} \RQA}
\newcommand{\rqTwo}{\textbf{RQ2.} \RQB}
%%\newcommand{\rqThree}{\textbf{RQ3.} \RQB}
%%\newcommand{\rqFour}{\textbf{RQ4.} \RQD}

\begin{itemize}
    \item \rqOne
    \item \rqTwo
\end{itemize}

The first research question addresses the distribution of subjects per
time cost. We are interested on identifying time-consuming test suites
to investigate further their characteristics (\eg, type of application
and bottlenecks from execution) \Jbc{do we have more arguments?}.  The
second research question addresses our interest in understanding if
developers are aware of parallelism features from testing frameworks
available out-of-the-box through build systems (\eg, JUnit and TestNG
with Maven Surefire) and what setting are often used.

\Fix{distribution of execution
    time per test case. For each subject identified in the first
    research question, we investigate how balanced is the cost of the
    test suite in contrast to the cost of test cases and if there are
    subjects where the time cost is mostly dominated by a small
fraction of test cases.} \Fix{The third research question addresses
    the distribution of regression tests according to the use of
    computational resources.  We are interested in investigating if
regression test suites are CPU intensive and if there are
opportunities to improve performance. The RQ4 addresses}
\Fix{...elaborate...}

\Comment{The rationale is that if the time cost
of a regression test is equally distributed among test cases, the
execution cost could be potentially improved by running tests in
parallel (in contrast to the scenario where only one test case
dominates most of the execution time).}

>>>>

\newcommand{\RQB}{How often do developers use parallelism to improve
runtime performance?}

\newcommand{\RQC}{What is the impact of parallalelization?}

\newcommand{\RQD}{What factors contribute to improve performance
through parallelization?\Jbc{Previously as "When does parallelization
works and when it does not so great?"}}

\newcommand{\RQE}{What are the limitations of parallelization?}

\newcommand{\rqOne}{\textbf{RQ1.} \RQA}
\newcommand{\rqTwo}{\textbf{RQ2.} \RQB}
\newcommand{\rqThree}{\textbf{RQ3.} \RQC}
\newcommand{\rqFour}{\textbf{RQ4.} \RQD}
\newcommand{\rqFive}{\textbf{RQ5.} \RQE}

\begin{itemize}
    \item \rqOne
    \item \rqTwo
    \item \rqThree
    \item \rqFour
    \item \rqFive
\end{itemize}

@@

The first research question addresses the distribution of subjects per
time cost. We are interested in identifying time-consuming test suites
to investigate further their characteristics (\eg, type of application
and bottlenecks from execution) \Jbc{do we have more arguments?}.  The
second research question addresses our interest in understanding if
developers are aware of parallelism features from testing frameworks
available out-of-the-box through build systems (\eg, run JUnit test
cases in parallel using Maven Surefire) and what setting are often
used. The third research question addresses the impact of parallelism
on the regression tests from our sample set. We are interested in
compare the execution performance with different parallel settings
(see Section~\ref{sec:modes}). The fourth research question addresses
the characteristics of regression tests from the previous experiment.
More specifically, we want to investigate if there is a relation
between the balance of test execution (\ie, how uniformly distributed
is the execution time across tests cases) and the usage of
computational resources (\ie, if tests are mostly CPU or IO intense)
that impacts the effectiveness of parallelization. Finally, the fifth
research question discusses the limitations and insights to overcome
the pitfalls of parallelization.

\Comment{
    \Fix{distribution of execution time per test case. For each subject
    identified in the first research question, we investigate how
    balanced is the cost of the test suite in contrast to the cost of
    test cases and if there are subjects where the time cost is mostly
    dominated by a small fraction of test cases.} \Fix{The third research
    question addresses the distribution of regression tests according
    to the use of computational resources.  We are interested in
    investigating if regression test suites are CPU intensive and if there
    are opportunities to improve performance. The RQ4 addresses}
    \Fix{...elaborate...}

    The rationale is that if the time cost of a regression test is equally
    distributed among test cases, the execution cost could be potentially
    improved by running tests in parallel (in contrast to the scenario
    where only one test case dominates most of the execution time).
}
